---
title: "GlueCon Tweets"
runtime: shiny
output: html_document
---

```{r, include=FALSE}
library(RNeo4j)
graph = startGraph("http://localhost:7474/db/data/")

library(ggplot2)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Hashtags

Choose a hashtag to view which hashtags are used most with that hashtag.

```{r, echo=FALSE}
inputPanel(
  textInput("hashtag", label="Hashtag", value="gluecon")
)

renderPlot({
  query = "
  MATCH (h1:Hashtag)-[:TAGS]->(:Tweet)<-[:TAGS]-(h2:Hashtag)
  WHERE h1.name = {hashtag}
  RETURN h2.name AS hashtag, COUNT(*) AS count
  ORDER BY count DESC LIMIT 5
  "
  
  data = cypher(graph, query, hashtag=input$hashtag)
  ggplot(data, aes(x=hashtag, y=count)) + geom_bar(stat="identity")
})
```

## Users

Choose a user to view which users are most similar to that user based on hashtags.

```{r, echo=FALSE}
inputPanel(
  textInput("username", label="Username", value="_nicolemargaret")
)

renderTable({
  query = "
  MATCH (u:User)-[:POSTS]->(:Tweet)<-[:TAGS]-(h:Hashtag)-[:TAGS]->(:Tweet)<-[:POSTS]-(other:User)
  WHERE u.username = {username}
  WITH other.username AS user, COUNT(DISTINCT h) AS count, COLLECT(DISTINCT h.name) AS hashtags
  ORDER BY count DESC LIMIT 5
  RETURN user, hashtags
  "
  
  data = cypher(graph, query, username=input$username)
  
  for (i in 1:nrow(data)) {
    data[i, ]$hashtags = paste(data[i, ]$hashtags[[1]], collapse=", ")
  }

  data
})
```